---
title: "Twitter Clustering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, suppress = TRUE}
library(igraph)
library(dplyr)
library(lsa)
library(rtweet)
library(tidyr)
```

First pull everyone you follow and who is following you
```{r}
#get all my followers and people I follow
my_following <- get_friends('travluptuous')
#remove first column
my_following <- my_following[2]
my_followers <- get_followers('travluptuous')

```

Remove everyone who you follow and they follow you back since (could create a separate list of these accounts since they are likely to be friends instead of large accounts). You are left with 'Non Mutuals'
```{r}
#get all the users I follow who dont follow me back
non_mutuals <- subset(my_following, !(user_id %in% my_followers$user_id))
non_mutuals <- as.list(non_mutuals$user_id)
#get all the users who I follow and they follow me back
mutuals <- subset(my_following, (user_id %in% my_followers$user_id))
mutuals <- as.list(mutuals$user_id)
```

Create a dataframe of all the non mutuals and everyone they follow, this can take a while due to rate limits
```{r}
#create data frames for all the non_mutuals with who they follow
#commenting out for now
for (i in non_mutuals) {
  assign(paste0('df_', i), get_friends(i, retryonratelimit = TRUE))

}
#create a copy of the dataframe
user_df<- df_103130238 


```

Remove anyone with less than 650 followers and add them to the mutual list. Arbitrarily set in order to try and remove users who are small accounts but just don't follow you back
```{r}
user_df_filtered <- user_df
filtered_users <- c()
non_mutuals_filtered <- non_mutuals
```

```{r}
for (i in non_mutuals) {
  if (nrow(user_df %>% filter(user == i)) < 600){
  user_df_filtered <- user_df_filtered %>% filter(user != i)
  filtered_users <- append(filtered_users, i)
  non_mutuals_filtered <- non_mutuals_filtered[non_mutuals_filtered != i]
  }
}

```

Create an empty symmetric matrix to populate as the adjacency matrix
```{r}
#create an empty matrix n_users x n_users
user_matrix <- matrix(data = 0, nrow = length(non_mutuals_filtered), ncol = length(non_mutuals_filtered))
```


Each row is a user and each column is a user, for each row set the value to 1 for every user that the row is following that exists in the non mutuals list
```{r}

#loop through each user
for (i in non_mutuals_filtered){
  #loop through all the followers 
  for (j in non_mutuals_filtered){
    #check each element of j to see if they are followed by i
    #filter the df to only be i's followers
    i_following <- user_df_filtered %>% filter(user == i)
    i_following_list <- as.list(i_following$user_id)
    for (k in i_following_list){
      if (j == k) {
        idx_c <- match(j,non_mutuals_filtered)
        idx_r <- match(i,non_mutuals_filtered)
        user_matrix[idx_c, idx_r] <-  1
      }
    }
  }
}
```

create an undirected graph from the adjacency matrix
```{r}
user_graph_undirected_orig <- graph_from_adjacency_matrix(user_matrix, mode = 'undirected')
user_graph_undirected_orig <- simplify(user_graph_undirected_orig, edge.attr.comb = 'sum')
```

Get a cleaner list of the users
```{r}
user_list <- c()
for (i in 1:length(non_mutuals_filtered)){
  user_list <- append(user_list, non_mutuals_filtered[[i]])}
```


Remove unconnected nodes
```{r}
iso_nodes <- which(degree(user_graph_undirected_orig) == 0)
iso_nodes
non_mutuals_filtered <- user_list[-iso_nodes]
user_graph_undirected <- delete.vertices(user_graph_undirected_orig, iso_nodes)

#user_graph_undirected <- user_graph_undirected_orig
coords <- layout_with_fr(user_graph_undirected)
```

Plot the basic graph
```{r  echo=FALSE}
plot(user_graph_undirected, edge.arrow.size = 0.2, layout=coords)
```


Greedy Community Detection

```{r}
cl_1 <- cluster_fast_greedy(user_graph_undirected)

```

Plot with background
```{r}
plot(cl_1, user_graph_undirected, layout=coords)
```
Plot just the colored nodes
```{r}
plot(user_graph_undirected, vertex.color=membership(cl_1), layout=coords)
```

Spectral Clustering

```{r}
cl_2 <- cluster_leading_eigen(user_graph_undirected)
```

Plot with background
```{r}
plot(cl_2, user_graph_undirected, layout=coords)
```

Plot just the clustered nodes
```{r}
plot(user_graph_undirected, vertex.color=membership(cl_2), layout=coords)
```


Get the membership of the clusters and create the list

Create a list of all the usernames for the ids
```{r}
user_names <- c()
for (i in non_mutuals_filtered){
  user <- lookup_users(i)
  user_names <- append(user_names, user$screen_name)
}
```

```{r}

df_list <- data.frame('users' = non_mutuals_filtered, 'clusters' = cl_2$membership, 'user_names' = user_names)

```

Now create the twitter lists, exlcude any small clusters (less than 10 users)
```{r}
for (i in 1:length(unique(cl_2$membership))) {
  df <- df_list %>% filter(clusters == i)
  #delete existing lists with the same name
  post_list(slug = paste0('list', i), destroy = TRUE)
  #filter out small lists
  if (nrow(df) > 10){
  users <- df$user_names
  post_list(users, paste0('list', i))
  }
}
```

